Latency-tolerant runtimes for large graph computations

### 2011-01-13 doc/hotpar2011/softxmt-hotpar2011.tex
conclusion

\documentclass{acm_proc_article-sp}
\begin{document}

@@

@@

Important 
Social networks
Facebook: 500M active users, 130 friends each on average. for
computing friend suggestions, 40-node cluster, 72GB/node, run every 2
days.

@@

@@

>>>>

\documentclass{acm_proc_article-sp}
\usepackage{url}
\begin{document}

@@

Many problems in bioinformatics and social networks

@@

Many

Social networks are an

Important 
Social networks

Social networks are

And social networkIn January 2011, Facebook had 500 million active users with an
average of 130 friends each \cite{Facebook:2011p91}. Facebook's
friend suggestion algorithm in 2010 ran on a 40-node cluster with 72GB
memory per node. Even with that capacity, new suggestions could only
be computed every two days \cite{Backstrom:2010p90}.

We

@@

replicate or partition

@@

Large irregular problems found in areas such as social networking and
bioinformatics tend to have poor performance on commodity clusters due
to freqent low-locality memory accesses. We present a programming
model and runtime system that uses lightweight context switching to
tolerate long-latency accesses and increase performance on these
applications. Our preliminary evaluation shows that the overhead of
context switching is not prohibitive for thread counts needed for a
large-scale implementation, but memory concurrency is limited by
hardware structures in commodity processors. We describe how we plan
to address the challenges of large-scale memory concurrency and
lightweight synchronization.

\bibliographystyle{acm}
\bibliography{softxmt-hotpar2011}
